---
output:
  html_document:
    toc: false
    toc_depth: 2
    theme: united
params:
  proj_path:
    value: "/Users/mf/2014_and_beyond/Side_projects/jiuJitsuCoaching/"
  file_name:
    value: "invoice_8.csv"
  private_rate:
    value: 44.8
  client:
    value: "SBG Portland"
  hourColumn:
    value: "Hours_worked"
  rate:
    value: 21
---

---
title: `r paste0(paste0("Invoice - ",month.abb[month(Sys.Date())]),format(Sys.Date(), ", %Y"))`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  results='show', warning=FALSE, message=FALSE, cache=FALSE, comment=NA)
```

```{r The_Libraries_Are_Open, echo = FALSE}
library(knitr)
require(data.table)
mainwd <- file.path(params$proj_path)
output_directory <- mainwd
```

---

Mark Fisher

609.577.9078

9421 North Portsmouth Avenue

Portland, OR 97203

---

```{r Main-section, echo = FALSE}
hour_table = fread(paste(params$proj_path,params$file_name, sep=""),stringsAsFactors=F)
hour_table = hour_table[!grepl("Private", Comments)]
# hour_table[,'Hours_worked', ] = round(hour_table[,'Hours_worked'],2)
totalHours = sum(hour_table[,params$hourColumn, with=F])
colnames(hour_table) = gsub("_", " ", colnames(hour_table))
kable(hour_table, caption = "Tracked Hours")
```

---

```{r Privates-section, echo = FALSE}
hour_table = fread(paste(params$proj_path,params$file_name, sep=""),stringsAsFactors=F)
hour_table = hour_table[grepl("Private", Comments)]
hour_table[,'Hours_worked'] = round(hour_table[,'Hours_worked'],2)
totalHoursPrivates = sum(hour_table[,params$hourColumn, with=F])
colnames(hour_table) = gsub("_", " ", colnames(hour_table))
kable(hour_table, caption = "Tracked Hours For Privates")
```

---

|Client|`r params$client`||||
|:---:|:---:|:---:|:---:|:---:|
|Date|`r Sys.Date()`||||
|For|SBG Coaching||||
|Total Hours Teaching|`r totalHours`||||
|Rate|$`r params$rate`/hr||||
|Total Hours Privates|`r totalHoursPrivates`||||
|Private Lesson Rate (after renewal discount and SBG share deducted)|$`r params$private_rate`/hr||||
|Amount Due|$`r (totalHours * params$rate)+(totalHoursPrivates * params$private_rate)`||||
|Payment Method|Check or PayPal: mark.aaron.fisher@gmail.com||||

---

